Knowledge and the Web: Homework 3

### 2015-11-12 homework_3/hw3.tex
vraag 2 begin added.
kaw

\begin{center}
	\Large
2. Which characteristics of a politician and his country influence the amount of TV appearances he makes?
\end{center}

>>>>

\begin{center}
	\Large
2. Which characteristics of a politician influence the amount of TV appearances he makes?
\end{center}

There is one specific characteristic that we really want to research. Namely: "Does the country of origin of the politician influence his TV appearences?".

\begin{center}
	\Large
3. Which politicians have a high chance of being murdered?
\end{center}
